Probabilistic hierarchical modeling of exoplanet populations using incomplete catalogs

### 2013-11-20 document/ms.tex
adding list of parameters and updating PGM

\usepackage{url}
\usepackage{algorithmic,algorithm}

@@

blah.

>>>>

\usepackage{url}
\usepackage{algorithmic,algorithm}
\usepackage{multirow}

@@

\section{A toy model}

We start by assuming that ever target star has some $K$ orbiting planets.
Most of these planets are unobserved because they are two small to be
detectable or because of geometry.
The graphical model in \fig{gm} is a sketch of the hypothetical generative
procedure for a catalog of exoplanet observations.
The way it is shown, this model is extremely general but we will consider a
very specific form here.
In \fig{gm} the global ``hyper'' parameters are:
\begin{itemize}
\item{the parameters describing the distributions of the exoplanet population
\population, and}
\item{the parameters of a model of the catalog's exoplanet selection function
\selection.}
\end{itemize}
Similarly, the ``hidden variables'' are:
\begin{itemize}
\item{the physical parameters of the star and the stellar system
\stellar---including the stellar mass and radius, a measure of the stellar
variability, and the mean inclination of the orbiting exoplanets---and}
\item{the physical parameters of an exoplanet \planet---period, radius, and
relative inclination.}
\end{itemize}
Finally, the observables are

\begin{figure}[htbp]
\begin{center}
    \includegraphics{gm.pdf}
\end{center}
\caption{%
\figlabel{gm}}
\end{figure}

\begin{deluxetable}{ccl}
\tablecaption{%
A description of the model parameters.
\tablabel{parameters}}
\tablewidth{0pt}
\tablehead{& & \colhead{Description}}
\startdata
\multirow{3}{*}{\population}
& $\population_\period$ & The period distribution \\
& $\population_\radius$ & The exoplanet radius distribution \\
& $\population_\relincl$ & The relative inclination distribution \\
\hline
\selection & --- & The parameters of the catalog selection function \\
\hline
$\isobs_{kn}$ & --- & A flag indicating the presence of exoplanet $k$ orbiting
star $n$ in the catalog \\
\hline
\multirow{3}{*}{$\planet_{kn}$}
& $\period_{kn}$ & The period of exoplanet $k$ orbiting star $n$ (or null) \\
& $\radius_{kn}$ & The exoplanet's radius \\
& $\relincl_{kn}$ & The inclination of this orbit away from the systemic mean \\
\hline
\multirow{3}{*}{$\planetobs_{kn}$}
& $\periodobs_{kn}$ & The observed exoplanet period and uncertainty \\
& $(\rorobs)_{kn}$ & The observed radius ratio and uncertainty \\
& $\impactobs_{kn}$ & A constraint on the observed impact parameter \\
\hline
\multirow{4}{*}{$\stellar_{n}$}
& $\smass_{n}$ & The mass of star $n$ \\
& $\sradius_{n}$ & The radius of star $n$ \\
& $\snoise_{n}$ & The ``variability'' of star $n$ \\
& $\incl_{n}$ & The mean inclination of the exoplanets in the system $n$ \\
\hline
\multirow{2}{*}{$\stellarobs_{n}$}
& $\sloggobs_{n}$ & The observed surface gravity (and uncertainty) of star $n$ \\
& $\snoiseobs_{n}$ & The estimated variability of star $n$ \\
\enddata
\end{deluxetable}
